\documentclass{article}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}

\usepackage[margin=1in]{geometry}
\usepackage[parfill]{parskip}
\setlength{\parindent}{.5in}

\begin{document}



\centerline{\sc \large Code Camp Challenge v5.0}
\vspace{.5pc}
\centerline{\sc Bell Tower Escape!}
\vspace{2pc}

\section*{Background}
Soon after Jurassic Park re-opened, some of the dinosaurs were purchased by the Pillsbury family for a Minneapolis branch of Jurassic Park. Unfortunately, they escaped and have made their way to the GMI campus. During an East Wing wide meeting on every floor of the Bell Tower involving network latency, the dinosaurs started getting in...! Due to the inciting panic, and velociraptors taking over the lower levels of the stair well (the doors only open inwards - so there's nothing to worry about!), the Bell Tower Elevators have been overloaded with people trying to get away from the trapped velociraptors and other people trying to get out of the building - as such, they need to be reporgrammed.

Each bank of the elevators are controlled by a different microcontroller, and elevator engineers have asked you to program one of them, and another colleague to program the other. They figured one of your algorithms will be efficient enough to get everyone where they want on time!

\section*{Game Information}
You get to control three elevators that go up and down the ten floors. You know what floor people are on and find out what floor they are trying to get to once they enter your elevator. Each turn consists of either moving an elevator up a floor, down a floor, or allowing people to get on or off (people will get on and off in the same turn). If an elevator from both banks opens on the same floor, the group will go for the elevator with fewer people, until the elevator's capacity is met, then people will go into a different elevator.

\section*{Issues}
For any issues, please put create an issue on our GitHub page (https://github.com/eonarheim/BellTowerEscape)

\end{document}